---
title             : ["Lexical, numeric"]
shorttitle        : "lexical, numeric"

author: 
  - name          : "Alex O. Holcombe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychology, Brennan MacCallum Bldg (A19), The University of Sydney, Sydney, NSW 2006, Australia"
    email         : "alex.holcombe@sydney.edu.au"


affiliation:
  - id            : "1"
    institution   : "School of Psychology, The University of Sydney"

author_note: > 
  This manuscript was written in RMarkdown using the *papaja* package [@R-papaja].

abstract: >
  As awareness of reproducibility problems in psychology have grown, new policies and norms for journals and for the practice of science have been proposed, and some have been implemented. Some of these prescriptions concern how replications should be planned, performed, and discussed <!-- [e.g., @pashler_taking_2017; @simons_introduction_2014]-->. These prescriptions have however not been fully justified. One is the claim that original authors, after a failure to replicate  their work, are obliged to do a follow-up experiment if they propose a particular sort of explanation of the failure to replicate. Fully justifying this and certain other prescriptions requires a broader discussion of where scientific responsibilities come from and how they are enforced. While some policies should await that discussion, we argue that one particular policy is relatively easy to justify. This is the policy of journals to solicit input of the original authors before an important large-scale replication study is conducted. Others have emphasized that original authors commenting before the replication study can improve the design of the study. We argue that what may be just as important is the benefits these comments have for other researchers, and that comments made after the replication results are known do not provide the same benefit.
  
keywords          : "lateralization, hemispheric, lexical"
wordcount         : "~10,000"  #Count the words from the terminal by 

bibliography      : ["referencesInfo/r-references.bib","referencesInfo/references.bib"] 

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

<!--
# Highlights (most should be worked into the Introduction somewhere, to tantalize)

* Even when the original and replicating authors are in complete agreement regarding the quality of a replication experiment before the data come in, their views can diverge widely upon seeing the data, for good reasons.

* The differing reactions of an original author and replicating authors are explained in a rational Bayesian framework.

* The differing reactions of believers and skeptics can be minimized by manipulation checks and other steps to reduce the number of auxiliary hypotheses.

* If the believers blame an auxiliary hypothesis, while the skeptics don't, this still can be an important scientific advance, but we must design an experiment so that the number of auxiliaries whose p is much less than one is very few.

* The original researcher knows things that others don't. We have to elicit that knowledge. Once the data are in, it may be very difficult to determine what the original and the replicator were in agreement on before the data came in. Thus it is important to elicit the views of both before the data come in.

* Suggestions that it is the "responsibility" of researchers to do one thing or another in response to a replication failure are misguided
-->

<!--
# Outline

1. The original researcher knows things that others don't.
2. After the data come in, motivated reasoning may contaminate researcher responses, impairing the ability to learn from the original authors' knowledge.
  + (the bad kind or the rational kind)
  + Enemies
3. Subjective beliefs are important to the progress of science
  + Trying to get objective probabilities of the hypotheses is not feasible.
  + Humans do science, so subjective beliefs determine allocation of scientific resources.


@barrett_opinion_2015
-->
# Introduction

> Science is organized skepticism in the reliability of expert opinion - R. P. Feynman, quoted by @smolin_trouble_2007, p.
307 

> Behavioral and neuroimaging evidence suggests that females have greater bilateral cerebral organization, particularly in language processing regions, whereas males show greater left-hemisphere dominance (Kansaku, Yamaura, & Kitazawa, 2000 Kansaku, K., Yamaura, A., & Kitazawa, S. (2000). Sex differences in lateralization revealed in the posterior language areas. Cerebral Cortex, 10, 866–872.10.1093/cercor/10.9.866
[Crossref], [PubMed], [Web of Science ®], [Google Scholar]
; McGlone, 1980 McGlone, J. (1980). Sex differences in human brain asymmetry: A critical survey. Behavioral and Brain Sciences, 3, 215–263. doi:10.1017/S0140525X00004398.
[Crossref], [Web of Science ®], [Google Scholar]
)

```{r test-main1, child = 'misguided.Rmd'}
```

```{r test-main2, child = 'recommendations.Rmd'}
```

```{r test-main2, child = 'conclusionsSummary.Rmd'}
```

\newpage

<!-- These lines ensure references are set with hanging indents in PDF documents; they are ignored in Word. -->
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
