---
title             : ["Lexical, numeric"]
shorttitle        : "lexical, numeric"

author: 
  - name          : "Alex O. Holcombe"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychology, Brennan MacCallum Bldg (A19), The University of Sydney, Sydney, NSW 2006, Australia"
    email         : "alex.holcombe@sydney.edu.au"


affiliation:
  - id            : "1"
    institution   : "School of Psychology, The University of Sydney"

author_note: > 
  This manuscript was written in RMarkdown using the *papaja* package [@R-papaja].

abstract: >
  As awareness of reproducibility problems in psychology have grown, new policies and norms for journals and for the practice of science have been proposed, and some have been implemented. Some of these prescriptions concern how replications should be planned, performed, and discussed <!-- [e.g., @pashler_taking_2017; @simons_introduction_2014]-->. These prescriptions have however not been fully justified. One is the claim that original authors, after a failure to replicate  their work, are obliged to do a follow-up experiment if they propose a particular sort of explanation of the failure to replicate. Fully justifying this and certain other prescriptions requires a broader discussion of where scientific responsibilities come from and how they are enforced. While some policies should await that discussion, we argue that one particular policy is relatively easy to justify. This is the policy of journals to solicit input of the original authors before an important large-scale replication study is conducted. Others have emphasized that original authors commenting before the replication study can improve the design of the study. We argue that what may be just as important is the benefits these comments have for other researchers, and that comments made after the replication results are known do not provide the same benefit.
  
keywords          : "lateralization, hemispheric, lexical"
wordcount         : "~10,000"  #Count the words from the terminal by 

bibliography      : ["referencesInfo/r-references.bib","referencesInfo/references.bib"] 

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf
---

<!--
# Highlights (most should be worked into the Introduction somewhere, to tantalize)

* Psyc1002 


* The differing reactions of an original author and replicating authors are explained in a rational Bayesian framework.

* The differing reactions of believers and skeptics can be minimized by manipulation checks and other steps to reduce the number of auxiliary hypotheses.

* If the believers blame an auxiliary hypothesis, while the skeptics don't, this still can be an important scientific advance, but we must design an experiment so that the number of auxiliaries whose p is much less than one is very few.

* The original researcher knows things that others don't. We have to elicit that knowledge. Once the data are in, it may be very difficult to determine what the original and the replicator were in agreement on before the data came in. Thus it is important to elicit the views of both before the data come in.

* Suggestions that it is the "responsibility" of researchers to do one thing or another in response to a replication failure are misguided
-->

<!--
# Notes

PSYC1002 experiment notes https://docs.google.com/document/d/1vPoKG5z4owBklNDH-XSm_Zhi2blA9WXCo4xyxyPKalU/edit
OSF project with Preregistered method https://osf.io/6pa9s/


@barrett_opinion_2015
-->
# Introduction


> Behavioral and neuroimaging evidence suggests that females have greater bilateral cerebral organization, particularly in language processing regions, whereas males show greater left-hemisphere dominance (Kansaku, Yamaura, & Kitazawa, 2000 Kansaku, K., Yamaura, A., & Kitazawa, S. (2000). Sex differences in lateralization revealed in the posterior language areas. Cerebral Cortex, 10, 866–872.10.1093/cercor/10.9.866
[Crossref], [PubMed], [Web of Science ®], [Google Scholar]
; McGlone, 1980 McGlone, J. (1980). Sex differences in human brain asymmetry: A critical survey. Behavioral and Brain Sciences, 3, 215–263. doi:10.1017/S0140525X00004398.
[Crossref], [Web of Science ®], [Google Scholar]
)

# Methods

OSF project with Preregistered method https://osf.io/6pa9s/

Full set of conditions were:
1.	Words, horizontally arrayed
2.	Words, vertically arrayed
3.	Letters (normal upright orientation), horizontally arrayed
4.	Letters (normal upright orientation), vertically arrayed
5.	Letters (mirror-reversed; that is, written backwards), horizontally arrayed
6.	Letters (rotated 90 deg clockwise; that is, facing downwards), vertically arrayed
7.	Letters (rotated 90 deg anticlockwise; that is, facing upwards), vertically arrayed

```{r methods, child = 'methods.Rmd'}
```


# Results

Look for results in the analysis git folder

From an email to Caleb: When participants saw (3 letter words) words oriented left to right the accuracy for the left word was 65.7% and the accuracy for the right word was 70.6%.

When participants saw (3 letter words) words oriented left to right (but presented top and bottom) the accuracy for the top word was 71.0% and the accuracy for the bottom word was 37.6%.

```{r test-main2, child = 'conclusionsSummary.Rmd'}
```

\newpage

<!-- These lines ensure references are set with hanging indents in PDF documents; they are ignored in Word. -->
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
