---
title: "analyseAll"
author: "Alex Holcombe"
date: "7/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

## Load data

```{r load file}
library(readr)
dataWithPath<- file.path("dataAnonymized","PSYC1anonymized")

#tb<- read_csv(  paste0(dataWithPath,".csv") )
tb<- readRDS( paste0(dataWithPath,".rda") )

#add practice column
practiceTrials = 5
tb<- tb %>% mutate(practice= (trialnum<practiceTrials))

```

Install skimr
```{r pressure, echo=FALSE}
#devtools::install_github("ropenscilabs/skimr")
#install.packages("tidyselect")  and from source to get 0.2.4 needed
library(skimr)
```

## Inspect data
```{r i, echo=FALSE}
skim(tb)
```

Load ggplot and dplyr
```{r j, echo=FALSE}
library(ggplot2)
library(dplyr)

tb<- tb %>% mutate(leftTopBias = case_when(spatial == "horiz" ~ correct0 - correct1,
                                          spatial == "vert" ~ correct1 - correct0,   
                                          TRUE ~ as.integer(-99)   )) #else, but this shouldn't occur

tb<- tb %>% mutate(canonical = ori==0) 

```

## Proportion correct

One target.
Why when rightResponseFirst == True, almost always scored as incorrect, correct0 = 0? (indicating subject got it wrong?). Probably didn't match the response0 to the correct stimulus, instead still matched it to the  letter on the left/top. And unfortunately didn't record the letter/word on the other side. To fix, have to write python script to rerun the code with the same seed to find out what letters they were, and then integrate with my tibble. Jesus.

```{r k, echo=FALSE}
#Look at one-target performance
tbOne <- tb %>% filter(oneTarget == "True") 
#correct0 refers to left, correct1 to right.
#But for one-target trials, rightResponseFirst is the only thing that tells you which side it was on.
eachCorrOne<- tbOne %>% group_by(rightResponseFirst) %>% summarise_at(c("correct0","correct1"),mean)
print(eachCorrOne)
```

Two targets

```{r Overall average correct, echo=FALSE}
#Exclude trials with one target, three targets
tbTwo <- tb %>% filter(oneTarget == "False", numSimultaneousStim < 3) 
#correct0 refers to left, correct1 to right.
eachCorrect<- tbTwo %>% summarise_at(c("correct0","correct1"),mean)
print(eachCorrect)
avgCorrect = rowMeans(eachCorrect)
```

```{r inspectStaircase}

#Inspect what ISIframes got up to

maxPossibleISIframes <- 9
maxEachSubject<- tb %>% filter(practice==0) %>% group_by(subject) %>% summarise(maxISI = max(ISIframes))
#Determine subject numbers who maxxed out
maxedOut <- unique(  tb %>% filter(ISIframes == maxPossibleISIframes)   )
ggplot(maxEachSubject, aes(x=maxISI)) + geom_histogram(binwidth=.5) +scale_x_continuous(breaks=seq(2,9))
```


```{r Exclude}
#Exclusion criteria
correctExclusionThreshold <- .4
#Exclude trials with one target, three targets
tbTwo <- tb %>% filter(oneTarget == "False", numSimultaneousStim < 3) 
#correct0 refers to left, correct1 to right.
overall<- tbTwo %>% group_by(subject) %>% summarise_at(c("correct0","correct1"),mean)
overall <- overall %>% mutate(pCorr = (correct0 + correct1)/2)
tooLow2 <- overall %>% filter(pCorr < correctExclusionThreshold)
cat("subjects who were too low in two-target condition are:")
tooLow2

#Exclude low performers in the 3-target condition
tbThree <- tb %>% filter(numSimultaneousStim == 3) 
overall<- tbThree %>% group_by(subject) %>% summarise_at(c("correct0","correct1","correct2"),mean)
overall <- overall %>% mutate(pCorr = (correct0 + correct1 + correct2)/3)
tooLow3 <- overall %>% filter(pCorr < correctExclusionThreshold)
cat("subjects who were too low in three-target condition are:")
tooLow3

```

```{r Calculate how many swaps each subject has}

#Compare response0 to 
#
```

```{r plotEach}
#Group by condition, which is defined by spatial,stimType,flipped,orient
#table(tbTwo$spatial,tbTwo$flipped,tbTwo$ori,tbTwo$stimType)
#Then plot difference between correct0 and correct1. One way to get difference is subtract correct1 from correct0 and average
#tbTwo$leftBtmBias <- tbTwo$correct0-tbTwo$correct1


tbTwo <- tbTwo %>% mutate(flippedTemp = substr(flipped,1,1)) #reduce to first letter only
tbTwo <- tbTwo %>% mutate(cond = paste(stimType, spatial, ori, flipped, sep = '_'))
tbTwo <- tbTwo %>% mutate(condExceptStim = paste(spatial, ori, flippedTemp, sep = '_'))
gg<- ggplot(tbTwo, aes(x=condExceptStim,y=leftTopBias)) + stat_summary(fun.y="mean",geom="point",size=2, alpha=.5) + facet_grid(stimType~.)
gg<- gg+ stat_summary(fun.data="mean_cl_boot",fun.args=list(conf.int=0.95),geom="errorbar",width=.3,size=1) 
show(gg)
```

```{r nicerPlot}
ltrs2 <- tbTwo %>% filter(stimType=="letter")
gg<- ggplot(ltrs2, aes(x=condExceptStim,y=leftTopBias)) + stat_summary(fun.y="mean",geom="point",size=2, alpha=.5) + facet_grid(.~canonical)
gg<- gg+ stat_summary(fun.data="mean_cl_boot",fun.args=list(conf.int=0.95),geom="errorbar",width=.3,size=1) 
show(gg)

ltrs2<- ltrs2 %>% mutate(cond = case_when(condExceptStim == "vert_-90_F" ~ "facing up",
                                        condExceptStim == "vert_90_F" ~ "facing down", 
                                        condExceptStim == "vert_0_F" ~ "facing right",
                                          TRUE ~ "unknown"   )) #e
rotated <- ltrs2 %>% filter(canonical==FALSE)
gg<- ggplot(rotated, aes(x=condExceptStim,y=leftTopBias)) + stat_summary(fun.y="mean",geom="point",size=2, alpha=.5) + stat_summary(fun.data="mean_cl_boot",fun.args=list(conf.int=0.95),geom="errorbar",width=.3,size=1) 
show(gg)


vertical<- ltrs2 %>% filter(spatial=="vert")
papaja::apa_beeplot(data=vertical, id="subject", dv="leftTopBias", factors="cond",
                    ylab = "upper - lower (proportion correct)", xlab = "orientation",
                    args_points = list(cex = 1, bg = c("black"),col="black"),
                    args_swarm = list(cex = .3, bg = c("white"),col="grey50"),
                    , args_error_bars = list(lwd=2.2,length = 0.13))

```

```{r finalPlots}
papaja::apa_beeplot(data=rotated, id="subject", dv="leftTopBias", factors="cond",
                    ylab = "upper - lower (proportion correct)", xlab = "orientation",
                    args_points = list(cex = 1, bg = c("black"),col="black"),
                    args_swarm = list(cex = .3, bg = c("white"),col="grey50"),
                    , args_error_bars = list(lwd=2.2,length = 0.13))

horiz <- ltrs2 %>% filter(spatial=="horiz")
horiz<- horiz %>% mutate(cond = case_when(condExceptStim == "horiz_0_F" ~ "normal",
                                        condExceptStim == "horiz_0_T" ~ "mirror-reversed",   
                                          TRUE ~ "unknown"   )) 
#change order so normal appears first on plot
horiz$cond <- as.factor(horiz$cond)
horiz <- transform(horiz, cond=reorder(cond, flipped) )  #https://stackoverflow.com/a/3744432/302378
papaja::apa_beeplot(data=horiz, id="subject", dv="leftTopBias", factors="cond",
                    ylab = "left - right (proportion correct)", xlab = "orientation",
                    args_points = list(cex = 1, bg = c("black"),col="black"),
                    args_swarm = list(cex = .3, bg = c("white"),col="grey50"),
                    , args_error_bars = list(lwd=2.2,length = 0.13))
```

```{r ttest}
t_horiz <- t.test(
  x = (horiz %>% filter(cond == "normal"))$leftTopBias
  , y = (horiz %>% filter(cond == "mirror-reversed"))$leftTopBias
  , paired = FALSE
)

# Let's see what the apa_print() output looks like
papaja::apa_print(t_horiz)
```
```

Calculate spatial bias for each participant, then correlate the bias with their author score.
```{r correlate}

```