---
title: "analyseAll"
author: "Alex Holcombe"
date: "7/28/2018"
output: html_document
---

Measurements Jen took for the monitors and viewing distance in OTC are Monitor height: 29.5cm, monitor length: 52.5cm, Viewing distance: 54cm.

I suppose I will combine all the js records into the tibble that also contains the data. After all, need some of those fields to know the condition.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load data and improve column names

```{r load file}
#rawDataPath<- file.path("practiceData","one")
rawDataPath<- file.path("practiceData")
source(file.path("readInAllFiles.R"))

#loadOneSession("practiceData","bleo3225_01Aug2018_12-40.txt")

tbAll<- readInAllFiles(rawDataPath)

tbAll <- rename(tbAll, "firstReadLang" = "What is the first language you learned to read?")
tbAll <- rename(tbAll, "handedness" = "Which is your dominant hand for common tasks,\nlike writing, throwing, and brushing your teeth?\n\n")
```

Anonymise subject names

```{r }
Ss <- unique(tbAll$subject)
listOfFakeNames <- 1:length(Ss)

#Permute to create random correspondence with codes
#Get a reproducible random seed so investigator can reverse to recover subject unikey if necessary
seed <- read_csv('subjectEncryptionKeyNotIndexedByGit/seed.csv')
seed <- seed$seed
set.seed(seed)
listOfFakeNames <- sample(listOfFakeNames)

#Replace real subject names by codes
#Create lookup table
lookup<- data.frame(old=Ss, new=listOfFakeNames)

newS <- tbAll$subject #new subject list
newS[] <- lookup$new[match(unlist(newS), lookup$old)] #https://stackoverflow.com/a/35636836/302378

tbAll$subject <- newS

```


Save data
```{r save file}
library(readr) #has better than save.csv https://readr.tidyverse.org/reference/write_delim.html
pathToSave <- file.path("dataAnonymized")
#saveRDS(tbAll, file = file.path(pathTosave,"PSYC1anonymized.rda", compress="bzip2")
write_csv(tbAll, file.path(pathToSave,"PSYC1anonymized.csv"))
```

Install skimr
```{r pressure, echo=FALSE}
#devtools::install_github("ropenscilabs/skimr")
#install.packages("tidyselect")  and from source to get 0.2.4 needed
library(skimr)
```

## Inspect data
```{r i, echo=FALSE}
skim(df)
```

Load ggplot and dplyr
```{r i, echo=FALSE}
library(ggplot2)
library(dplyr)
```

## Proportion correct

```{r i, echo=FALSE}
notOneTarget
eachCorrect<- df %>% summarise_at(c("correct0","correct1"),mean)
avgCorrect = rowMeans(eachCorrect)
```

```{r}
if (avgCorrect < .5) {
  shouldExclude = TRUE
}
practiceTrials = 3
df$experimentPhase<-NULL
df<- df %>% mutate(practice= trialnum<=2)
#Sanity check what ISIframes got to
longestISIframes<- max( df %>% filter(practice==0) %>% select("ISIframes") )
S<-data.frame()
S$name<-df$subject[1]
```
