---
title: "threeLetterTask"
author: "Alex Holcombe"
date: "8/14/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Run after demographicsAndExclusions.Rmd

```{r pressure, echo=FALSE}
library(dplyr)
three <- tc %>% filter(numSimultaneousStim==3) %>% filter(practice==FALSE)
```

Num Ss = `r length(unique(three$subject))`

Print % correct

```{r ok, echo=FALSE}
#Average across Ss first, then average subject averages
three %>% group_by(subject) %>% summarise_at(c("correct0", "correct1","correct2"), mean, na.rm = TRUE) %>% 
  summarise_at(c("correct0", "correct1","correct2"), mean, na.rm = TRUE) 
```

Do exclusions

"Participants will be excluded if their performance is less than 40% correct in the trials after excluding the one-target trials (the experiment uses a staircase that targets 71% correct, but it may take many trials for the staircase to reach their level if they require a long ISI to see the stimulus)."

"Consistently ignoring the instruction to report a particular side first (on each trial, they are told to report one of the stimuli first). This will be assessed by counting as correct all responses that match the stimulus regardless of side, and more than 30% of these being location swaps are grounds for exclusion."

This swap criterion seems pretty weak, but it's a balance between excluding swappers and precluding the possiblity that real swaps occur often even when trying to follow instructions.

```{r excludeLowerPerformers, echo=FALSE}
th<- three %>% group_by(subject) %>% mutate(avgCorr = (correct0 + correct1 + correct2)/3)
ti <- th %>% group_by(subject) %>% summarise_at("avgCorr", mean)
losers <- ti %>% filter(avgCorr<.4)
print(losers)

losers <- as.numeric( unique(losers$subject) )

#convert subject to numeric
Ss <- three$subject
three$subject<- as.numeric(Ss)

#convert losers to numeric

# filter(!(subject %in% losers) )
three<- three %>% filter(  !(subject %in% losers)   )

#kludge because know there is only one loser.
#three<- three %>% filter(subject != as.numeric(losers[1]))
```

Exclude swappers
```{r excludeSwappers, echo=FALSE}
#Count as a swap both answer0 = response2 and  answer2 = response0
#To include middle swaps, count as answer0 = response1, answer1 = response0, answer2=response1, answer1 = response2

#Delete irrelevant columns
swap <- three %>% select(subject,starts_with("ans"),starts_with("resp"),starts_with("corr"))
swap <- swap %>% mutate(swap02 = (answer0==response2) & (response2!=answer2)) #matches other one and is not correct (which can happen with repetitions)
swap <- swap %>% mutate(swap20 = (answer2==response0) & (response0!=answer0)) #matches other one and is not correct (which can happen with repetitions)
swap <- swap %>% mutate(swap01 = (answer0==response1) & (response1!=answer1)) #matches other one and is not correct (which can happen with repetitions)
swap <- swap %>% mutate(swap10 = (answer1==response0) & (response0!=answer0)) #matches other one and is not correct (which can happen with repetitions)
swap <- swap %>% mutate(swap12 = (answer1==response2) & (response2!=answer2)) #matches other one and is not correct (which can happen with repetitions)
swap <- swap %>% mutate(swap21 = (answer2==response1) & (response1!=answer1)) #matches other one and is not correct (which can happen with repetitions)

#Add up how many swaps.  answer   A B C
#                        response C B B   - one swap
swap<-swap %>% mutate(swaps = swap02+swap20+swap01+swap10+swap12+swap21)
#Maximum that happened = 4.
# answer  A B A
#response B A B   Makes 4 swaps. But should we allow swaps to multiple locations from same answer?
#In this case, 2 is swapped to both 1 and to 3
# A more restrictive definition of swapping would be just the 3 different ways you could report the 3 letters, 012, 120, 201, plus getting one letter in right position would be 210, 
#And then want to allow for getting one letter wrong.

#For now, just look at incidence of swap>=2
```

```{r calculateSwapper, echo=FALSE}
swap<-swap %>% mutate(twoOrMore = swaps>=2)

ti <- swap %>% group_by(subject) %>% summarise_at(c("twoOrMore","swaps"), mean)

ti <- swap %>% group_by(subject) %>% summarise_at("swaps", mean)
library(ggplot2)
ggplot(ti, aes(x=swaps)) + geom_histogram()
ggplot(ti, aes(x=twoOrMore)) + geom_histogram()
swappers <- ti %>% filter(twoOrMore>.2)
print(swappers)
swappers <-  unique(swappers$subject)

```


```{r saveDataForJen, echo=FALSE}
swappers<- as.numeric(swappers)
afterExclusions<- three %>% filter(  !(subject %in% swappers)   )
```

```{r, echo=FALSE}
collapsed <- afterExclusions %>% group_by(subject) %>% summarise_at(c("correct0", "correct1","correct2"), mean, na.rm = TRUE)
oneTwo <- t.test(
  x = collapsed$correct0
  , y = collapsed$correct1
  , paired = FALSE
)
oneTwo

twoThree <- t.test(
  x = collapsed$correct1
  , y = collapsed$correct2
  , paired = FALSE
)
twoThree

```

Look at language.
```{r, echo=FALSE}
  
# summarise_all(funs(if_else(is.numeric(.), mean(.), first(.)))) #Why doesn this give error?

collapsedSubjLang <- three %>% group_by(subject,firstReadLang) %>% summarise_at(c("correct0", "correct1","correct2"), mean, na.rm = TRUE)
collapsedSubjLang %>% group_by(firstReadLang) %>% summarise_all(mean)  #works

engSino <- t.test(
  x = (collapsedSubjLang %>% filter(firstReadLang=="Chinese"))$correct0
  , y = (collapsedSubjLang %>% filter(firstReadLang=="English"))$correct0 
  , paired = FALSE
)
engSino

engSino <- t.test(
  x = (collapsedSubjLang %>% filter(firstReadLang=="Chinese"))$correct1
  , y = (collapsedSubjLang %>% filter(firstReadLang=="English"))$correct1
  , paired = FALSE
)
engSino

engSino <- t.test(
  x = (collapsedSubjLang %>% filter(firstReadLang=="Chinese"))$correct2
  , y = (collapsedSubjLang %>% filter(firstReadLang=="English"))$correct2 
  , paired = FALSE
)
engSino


collapsed <- three %>% group_by(subject) %>% summarise_at(c("correct0", "correct1","correct2"), mean, na.rm = TRUE)

```

Save data for Jen
```{r}
dataWithPath<- file.path("dataAnonymized")
library(readr)
#currently without most columns, until learn how to preserve text columns etc when taking mean
write_tsv(collapsed, file.path(dataWithPath,"threeLetterTaskAfterExclusionsCollapsedSs.tsv"))
write_tsv(afterExclusions, file.path(dataWithPath,"threeLetterTaskAfterExclusions.tsv"))

```

Work out  how to save all non-numeric columns

#try keeping language only
cc <- three %>% select(correct0,correct1,correct2,firstReadLang)
#cc %>%  group_by(firstReadLang) %>% summarise_all(funs(if_else(is.numeric(.), mean(.), last(.)))) #Get error
three %>%  group_by(firstReadLang) %>% summarise_if( is.numeric, mean)
#collapsed %>% group_by(firstReadLang) %>%  summarise_at(c("correct0", "correct1","correct2"), mean, na.rm = TRUE)


```

Look at correlation. 


