---
title: "score authors"
author: "Alex Holcombe"
date: "7/27/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Read in a json file with the authors data and miscellaneous info.

```{r cars}
library(jsonlite)
js<- fromJSON(file.path("practiceData","alexh_27Jul2018_16-37authors.json"))
sel<- js$selected
length(sel)
```

Calculate the score on the author test. From Martin-Chang & Gould (2008), "Print exposure scores were calculated by subtracting the proportion of decoy names checked from the proportion of real authors correctly identified."

Import the key.
```{r check, echo=FALSE}
library('readr')#install.packages('readr')
fileWithPath<- file.path("..","inputFiles","authorsAndNonauthors.txt")
key <-read_tsv(fileWithPath)  #read_tsv from tidyverse readr has advantage of not having padding spaces
```
Calculate how many authors selected.

```{r , echo=FALSE}
numTested <- length(sel)
#get scoring key only for those tested, which is the first numTested of the whole key
keyThis<- key$author[1:numTested]
selWithAns <- data.frame(sel,keyThis)
#Use dplyr to select rows where keyThis ==1, then add up number selected
library(dplyr)
authors<- selWithAns %>% filter(keyThis==1)
maxScorePossible <- nrow(authors)

authorsChosen<- sum(authors$sel)

#Calculate how many non-authors selected
nonAuthors<- selWithAns %>% filter(keyThis==0)
nonAuthorsChosen <- sum(nonAuthors)
scoreRaw <- authorsChosen - nonAuthorsChosen
scorePct <- scoreRaw / maxScorePossible
```



What is split-half reliability?

